---
title: "Random Generation of Gene IDs and SNP Rate Calculation"
author: "Elena Venable"
date: "February 5, 2015"
output: html_document
---

## 1. Load the Necessary Data
Load a file containing all the gene_IDs and load `SexSpecificExpression`.

```{r}
library(SexSpecificExpression)
load("~/SexSpecificExpression/data/gene_IDs.rda")
load("~/SexSpecificExpression/data/compiled_SNP_data.rda")
```

This also requires the compiled genome data, which is explained in the vignette "SNPcount_functions."  The genome list is extracted from the output of the `all_chromosome` function.

```{r}
SNPs_and_genes <- all_chromosomes(compiled_SNP_data = compiled_SNP_data)
genome <- SNPs_and_genes$genome_with_SNP
```

## 2. Generate a Random List of Genes
Use the code below to generate a list of random genes for which calculate the SNP rate. The variable `n` is the number of samples in the random generation.

```{r}
n = 50000
gene_index <- sample(1:length(gene_IDs), n, replace=FALSE )
gene_names <- gene_IDs[gene_index]
```

## 3. Find the SNP Rate of the Random Gene List
Use the function `calculate_snp_rate` to find the SNP rate per base pair in the random gene generation.  A vector contain gene names (i.e the names of expressed genes) can also be input instead of a random list.

```{r}
snp_rate <- calculate_snp_rate(GeneIDs = gene_names,genome = genome)
snp_rate
```

